Lexicalized Domain Representations for Neural Machine Translation

### 2019-08-28 2019/iwslt/submission.tex
couple of late fixes

\begin{table}[h]
  \centering
%  \begin{tabularx}{1.0\linewidth}{c|c}
  \begin{tabular}{c|c}
    Polysemic ``words'' & Monosemic ``words'' \\ \hline
     ases (0) &               obtain (10) \\       
     impairment (1) &     virtually (10) \\    
     convenience (1) &    represent (10) \\    
     oring (1) &              safety (10) \\       
     ums (1) &               defence (10) \\      
     turnover (1) &         coordinated (10) \\  
     occurrence (1) &     handling (10) \\     
     tent (2) &               July (10) \\         
     ture (2) &               previous (10) \\     
     mation (2) &           better (10) \\ \hline
  \end{tabular}
  \caption{Analyzing the variation of embeddings across domains. Each word or subword is listed with the size of the intersection (between 0 and 10).}
  \label{tab:embeddings}
\end{table}

@@

Let us now consider the list of putative monosemic words (on the right part of Table~\ref{tab:embeddings}), ie.\ words for which the nearest neighbors are the same in all domains, contains mostly words for which we do not expect much variation in translation: adjective (``previous'', ``better''), adverbs (``virtually``), generic verbs (``handling'', ``coordinated''), etc; and the list of words having a constant set of neighbors also contains prepositions (``at'', ``in''), auxiliary (``been'') etc.

>>>>

\begin{table}[h]
  \centering
%  \begin{tabularx}{1.0\linewidth}{c|c}
  \begin{tabular}{c|c}
    Polysemic ``words'' & Monosemic ``words'' \\ \hline
     ases (0) &               obtain (10) \\       
     impairment (1) &     virtually (10) \\    
     convenience (1) &    represent (10) \\    
     oring (1) &              safety (10) \\       
     ums (1) &               defence (10) \\      
     turnover (1) &         coordinated (10) \\  
     occurrence (1) &     handling (10) \\     
     tent (2) &               July (10) \\         
     ture (2) &               previous (10) \\     
     mation (2) &           better (10) \\ \hline
  \end{tabular}
  \caption{Analyzing the variation of embeddings across domains. For each word or subword we also report the size of the intersection (between 0 and 10).}
  \label{tab:embeddings}
\end{table}

@@

Let us now consider the list of putative monosemic words (on the right part of Table~\ref{tab:embeddings}), ie.\ words for which the nearest neighbors are the same in all domains. This list contains mostly words for which we do not expect much variation in translation: adjectives (``previous'', ``better''), adverbs (``virtually``), generic verbs (``handling'', ``coordinated''). Further down this list, we will also find prepositions (``at'', ``in''), auxiliary (``been'') etc.
